Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-06-24 demystify.tex
updates

\paragraph{Acceptance Letters} Universities prioritize sending out acceptance letters first. This allows the admitted students to make decision and plan for their studies. These letters go to the top candidates who are offered admission directly without being placed on a waitlist.

@@

\paragraph{Response Deadlines} Accepted students are usually given a strict deadline to make decision on their offers, often around \textbf{April 15th} in the US. This is a standard deadline for PhD programs due to the Council of Graduate Schools (CGS) Resolution. After this date, programs can gauge how many slots remain unfilled.

>>>>

\paragraph{Acceptance Letters} Universities prioritize sending out acceptance letters first. This allows the admitted students to make decision and plan for their studies.

@@

\paragraph{Response Deadlines} Accepted students are usually given a deadline to make decision on their offers, often around around \textbf{April 15th} in the US. This is a standard deadline for PhD programs due to the Council of Graduate Schools (CGS) Resolution (\href{https://cgsnet.org/wp-content/uploads/2024/01/CGS_April15_Resolution_Jan312024.pdf}{see more). After this date, CS programs can gauge how many slots remain unfilled.
